Experiment 3 of 4

### 2017-05-16 experiments/e3/writeup/e3.Rmd
ggplot computes summary on the fly using mean_cl_boot

```{r loadLibraries, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R')
```

@@

```{r computeSummariesForGraphs, cache=TRUE, message=FALSE}
rtdataplot1 <- summarySEwithin2(rtdata, measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
```

```{r rtplot, fig.width=7, fig.height=3}
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1, aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

>>>>

```{r loadLibraries, message=FALSE}
library(knitr); library(MASS); library(ggplot2); library(lme4); library(xtable); library(plyr); library(lattice); library(LMERConvenienceFunctions); library(car); library(grid); library(lmerTest); library(reshape2); library(ggplot2); library(languageR); library(pander); source('summarySEwithin2.R'); library(Hmisc)
```

@@

```{r rtplot1, fig.width=7, fig.height=3}
# this plot uses a precomputed summary done by summarySEwithin
# and data trimmed at 2.5 sd per subject
rtdataplot1 <- summarySEwithin2(data=perSubjectTrim.fnc(rawdata, response='RT', subject='Subject', trim = 2.5)$data,
                                measurevar="RT_log", withinvars=c("Vagueness", "Selection", "Item"), idvar="Subject")
dodge = position_dodge(width=0.2)
rtdataplot1$Condition <- as.factor(paste(sep=' ', rtdataplot1$Selection, rtdataplot1$Vagueness))
rtplot=ggplot(rtdataplot1,
              aes(y=RT_logNormed, x=Item, ymin=RT_logNormed-ci, ymax=RT_logNormed+ci,
                group=Condition, shape=Condition, fill=Condition)) +
  geom_line(position=dodge) +
  geom_errorbar(width=.2, position=dodge) +
  geom_point(size=2, position=dodge) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  ggtitle("Response time") +
  ylab("Respone time (log (ms))") + 
  xlab("") +
  theme_bw() +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
        legend.key = element_blank(), aspect.ratio=1,
        axis.text.x = element_text(angle = 45, hjust = 1),
        plot.background=element_rect(fill=NA, color='white')) +
  facet_grid(~Selection) 
rtplot
```

```{r rtplotHmisc, fig.width=7, fig.height=3}
# n.b. rtdata has been trimmed at 2.5 sd: use rawdata if you want untrimmed data
rawdata$Condition <- as.factor(paste(sep=' ', rawdata$Selection, rawdata$Vagueness))
ggplot(rawdata, aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition)) + 
  stat_summary(fun.data = "mean_cl_boot", position=position_dodge(0.2)) +
  scale_shape_manual("",values = c(22, 22, 21, 21)) +
  scale_fill_manual("",values=c("black","white","black","white")) +
  facet_grid(~Selection)

  mapping = aes(y=RT_log, x=Item, group=Condition, shape=Condition, fill=Condition),
  stat = stat_summary(fun.data = "mean_cl_boot") )

ggplot(mtcars) +
  geom_pointrange
+
  facet_grid(~Selection)

d <- ggplot(mtcars, aes(cyl, mpg)) 
d + stat_summary(fun.data = "mean_cl_boot", colour = "red", size = 2)
# +
  # theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
  #       legend.key = element_blank(), aspect.ratio=1,
  #       axis.text.x = element_text(angle = 45, hjust = 1),
  #       plot.background=element_rect(fill=NA, color='white')
```
